30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-13 paper.tex
Fix itemize layout

	\section{Comparison existing decentralized networks}
		In the last section, we discussedexisting decentralized peer-to-peer networks. In this section we will make a comparison between these networks. For each network, we will explain the following features:
\begin{itemize}
\item Compatibility with Tor. If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
\item Public implementation. For each network we will explain whether a public implementation is available.
\item Used in practice. Is the network used in practice?
\item Attack resistance. We will explain the various weaknesses and possible attacks of each network.
\end{itemize}

>>>>

	\section{Comparison existing decentralized networks}
		In the last section, we discussedexisting decentralized peer-to-peer networks. In this section we will make a comparison between these networks. For each network, we will explain the following features:

		\begin{itemize}
			\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
			\item{Public implementation:} For each network we will explain whether a public implementation is available.
			\item{Used in practice:} Is the network used in practice?
			\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
		\end{itemize}
